EuPPollNet: A European database of plant-pollinator networks

### 2024-04-11 Manuscript/Ms.qmd
some text of taxonomic coverage... Still thinking how to best explain it

The database contains `r study_number` independent published and unpublished studies conducted during the time period `r min_year` - `r max_year` on `r country_number` different countries (**Figure 1a** and **Figure 1b**). The different studies differ in sampling effort and methodology, although most studies took place within a single flowering season (`r format(round(one_year, 2), nsmall = 2)`%), sampled a given location an average of `r format(round(average_sampling_days, 2), nsmall=2)` days, and documented interactions mostly by using `r  most_common_method[[1]]` as sampling method (`r format(round(most_common_method[[3]], 2), nsmall = 2)`%). The database includes a total of `r prettyNum(interaction_number, big.mark=",")` distinct interactions, considering interaction as the contact of a given pollinator to the reproductive structure of a particular plant, from `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator and `r prettyNum(plant_spp_number, big.mark=",")` plant species. Most of the pollinator species in the database belong to the orders Hymenoptera and Diptera, each comprising approximately 1,000 species. However, the majority of plant-pollinator interactions are from Hymenoptera species (`r format(round(Hymenoptera_interactions, 2), nsmall = 2)`%; **Figure 1c**).

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
poll_output = readRDS("../Data/Working_files/pollinator_sampling_coverage.rds")
plant_output = readRDS("../Data/Working_files/plant_sampling_coverage.rds")
int_output = readRDS("../Data/Working_files/interactions_sampling_coverage.rds")
plant_poll_output = readRDS("../Data/Working_files/plant_poll_spp_sampling_coverage.rds")

@@

#Increase doubling effort
##Pollinators
poll_increase = poll_output$iNextEst$Network_id
poll_increase1 = poll_increase %>% filter(method == "observed") %>% pull(qD)
poll_increase2 = poll_increase %>% filter(t == max(t)) %>% pull(qD)
poll_increase3 = (poll_increase2-poll_increase1)/poll_increase1 * 100
##Plants
plant_increase = plant_output$iNextEst$Network_id
plant_increase1 = plant_increase %>% filter(method == "observed") %>% pull(qD)
plant_increase2 = plant_increase %>% filter(t == max(t)) %>% pull(qD)
plant_increase3 = (plant_increase2-plant_increase1)/plant_increase1 * 100
##Interactions
int_increase = int_output$iNextEst$Network_id
int_increase1 = int_increase %>% filter(method == "observed") %>% pull(qD)
int_increase2 = int_increase %>% filter(t == max(t)) %>% pull(qD)
int_increase3 = (int_increase2-int_increase1)/int_increase1 * 100
##Pollinator by plant
plant_poll_increase = plant_poll_output$iNextEst$Plant_id
plant_poll_increase1 = plant_poll_increase %>% filter(method == "observed") %>% pull(qD)
plant_poll_increase2 = plant_poll_increase %>% filter(t == max(t)) %>% pull(qD)
plant_poll_increase3 = (plant_poll_increase2-plant_poll_increase1)/plant_poll_increase1 * 100
```

@@

The estimated sampling coverage of plant and pollinator species within the database across the different sampling sites is approximately `r round(poll_coverage)`% for both taxonomic groups. This suggest that the rarefied accumulation curves of both plant and pollinator species exhibit already a "quasi-asymptotic" growth of species richness by considering the current number of sampling sites or networks (**Figure 2a-2b**). The predicted observed species richness by doubling the sampling effort on the already sampled habitat types within the database will only increase pollinator richness by `r format(round(poll_increase3, 2), nsmall=2)`% and plant richness by `r format(round(plant_increase3, 2), nsmall=2)`%. However, the sampling coverage of interactions is `r format(round(int_coverage, 2), nsmall=2)`%, and by doubling the sampling effort the predicted number of unique interactions recorded will have approximately a twofold increase (`r format(round(int_increase3, 2), nsmall=2)`%; **Figure 2c**). Similarly, to the plant and pollinator species accumulation curves across sampling sites, when we consider the accumulated pollinator richness across sampled plant species, this curve also shows a "quasi-asymptotic" growth with a sampling coverage value of `r format(round(plant_poll_coverage, 2), nsmall=2)`%. The predicted increase of recorded pollinator species by sampling the double of plant species would be `r format(round(plant_poll_increase3, 2), nsmall=2)`%.

Maybe fix last graph? And add it 1st of the last panel (**Figure 2d**)

The majority of plant and pollinator species tend to be regionally specific, with only a minor portion of them being shared across a broad range of studies (**Figures 2e-2f**). For instance, xxxxxxxxx.

The estimated sampling coverage when we consider plants,

@@

@@

The database contains xxxx species of pollinators and xxxx species of plants. Most species of pollinators are Hymenoptera species (%), and most of these species are bees (%).

>>>>

The database contains `r study_number` independent published and unpublished studies conducted during the time period `r min_year` - `r max_year` on `r country_number` different countries (**Figure 1a** and **Figure 1b**). The different studies differ in sampling effort and methodology, although most studies took place within a single flowering season (`r format(round(one_year, 2), nsmall = 2)`%), sampled a given location an average of `r format(round(average_sampling_days, 2), nsmall=2)` days, and documented interactions mostly by using `r  most_common_method[[1]]` as sampling method (`r format(round(most_common_method[[3]], 2), nsmall = 2)`%). The database includes a total of `r prettyNum(interaction_number, big.mark=",")` distinct interactions, considering interaction as the contact of a given pollinator to the reproductive structure of a particular plant. Most of the pollinator species in the database belong to the orders Hymenoptera and Diptera, each comprising approximately 1,000 species. However, the majority of plant-pollinator interactions are from Hymenoptera species (`r format(round(Hymenoptera_interactions, 2), nsmall = 2)`%; **Figure 1c**).

@@

#Sampling coverage outputs
poll_output = readRDS("../Data/Working_files/pollinator_sampling_coverage.rds")
plant_output = readRDS("../Data/Working_files/plant_sampling_coverage.rds")
int_output = readRDS("../Data/Working_files/interactions_sampling_coverage.rds")
plant_poll_output = readRDS("../Data/Working_files/plant_poll_spp_sampling_coverage.rds")

@@

#Increase doubling effort
##Pollinators
poll_increase = poll_output$iNextEst$Network_id
poll_increase1 = poll_increase %>% filter(method == "observed") %>% pull(qD)
poll_increase2 = poll_increase %>% filter(t == max(t)) %>% pull(qD)
poll_increase3 = (poll_increase2-poll_increase1)/poll_increase1 * 100
##Plants
plant_increase = plant_output$iNextEst$Network_id
plant_increase1 = plant_increase %>% filter(method == "observed") %>% pull(qD)
plant_increase2 = plant_increase %>% filter(t == max(t)) %>% pull(qD)
plant_increase3 = (plant_increase2-plant_increase1)/plant_increase1 * 100
##Interactions
int_increase = int_output$iNextEst$Network_id
int_increase1 = int_increase %>% filter(method == "observed") %>% pull(qD)
int_increase2 = int_increase %>% filter(t == max(t)) %>% pull(qD)
int_increase3 = (int_increase2-int_increase1)/int_increase1 * 100
##Pollinator by plant
plant_poll_increase = plant_poll_output$iNextEst$Plant_id
plant_poll_increase1 = plant_poll_increase %>% filter(method == "observed") %>% pull(qD)
plant_poll_increase2 = plant_poll_increase %>% filter(t == max(t)) %>% pull(qD)
plant_poll_increase3 = (plant_poll_increase2-plant_poll_increase1)/plant_poll_increase1 * 100

#Prepare results from common and rare poll across sampling sites
#Pollinators
poll_spread = data %>% 
select(Pollinator_rank, Pollinator_accepted_name, Network_id) %>% 
group_by(Network_id) %>% 
filter(Pollinator_rank == "SPECIES") %>% 
distinct(Pollinator_accepted_name) %>% 
ungroup() %>% 
count(Pollinator_accepted_name) %>% 
rename(n_networks_shared = n) %>% 
arrange(-n_networks_shared) %>% 
mutate(Percent_total = n_networks_shared / n_distinct(data$Network_id)*100)
#Check number of studies under 1%
poll_total = nrow(poll_spread)
polls_under_one_percent = poll_spread %>% 
filter(Percent_total<1) %>% 
nrow()
polls_under_one_percent = polls_under_one_percent/poll_total * 100
#Find most common pollinator
most_common_poll = poll_spread %>% 
filter(Percent_total == max(Percent_total)) %>% 
pull(Pollinator_accepted_name)
#Find most common poll percent
most_common_poll_percent = poll_spread %>% 
filter(Percent_total == max(Percent_total)) %>% 
pull(Percent_total)
#Plants
plant_spread = data %>% 
select(Plant_rank, Network_id, Plant_accepted_name) %>% 
group_by(Network_id) %>% 
filter(Plant_rank == "SPECIES") %>% 
distinct(Plant_accepted_name) %>% 
ungroup() %>% 
count(Plant_accepted_name) %>% 
rename(n_networks_shared = n) %>% 
arrange(-n_networks_shared) %>% 
mutate(Percent_total = n_networks_shared / n_distinct(data$Network_id)*100)
#Check number of studies under 1%
plant_total = nrow(plant_spread)
plants_under_one_percent = plant_spread %>% 
filter(Percent_total<1) %>% 
nrow()
plants_under_one_percent = plants_under_one_percent/plant_total * 100  
#Find most common plant
most_common_plant = plant_spread %>% 
filter(Percent_total == max(Percent_total)) %>% 
pull(Plant_accepted_name)
#Find most common plant percent
most_common_plant_percent = plant_spread %>% 
filter(Percent_total == max(Percent_total)) %>% 
pull(Percent_total)
```

@@

The estimated sampling coverage of plant and pollinator species within the database across the different sampling sites is approximately `r round(poll_coverage)`% for both taxonomic groups. This suggest that the rarefied accumulation curves of both plant and pollinator species exhibit already a "quasi-asymptotic" growth of species richness by considering the current number of sampling sites or networks (**Figure 2a-2b**). The predicted observed species richness by doubling the sampling effort on the already sampled habitat types within the database will only increase pollinator richness by `r format(round(poll_increase3, 2), nsmall=2)`% and plant richness by `r format(round(plant_increase3, 2), nsmall=2)`%. However, the sampling coverage of interactions is `r format(round(int_coverage, 2), nsmall=2)`%, and by doubling the sampling effort the predicted number of unique interactions recorded will have approximately a twofold increase (`r format(round(int_increase3, 2), nsmall=2)`%; **Figure 2c**). Similarly, to the plant and pollinator species accumulation curves across sampling sites, when we consider the accumulated pollinator richness across sampled plant species, this curve also shows a "quasi-asymptotic" growth with a sampling coverage value of `r format(round(plant_poll_coverage, 2), nsmall=2)`%. The predicted recorded pollinator species by doubling the number of plants sampled is expected to increase by `r format(round(plant_poll_increase3, 2), nsmall=2)`% (**Figure 2d**). In addition, when we explore how common or rare are plant and pollinator species across all sampling sites, we find that the majority of plant and pollinator species tend to be regionally specific, and only a minor portion of them is being shared across a broad range of sampling sites (**Figures 2e-2f**). For instance, most plants (`r format(round(plants_under_one_percent, 2), nsmall=2)`%) and pollinators (`r format(round(polls_under_one_percent, 2), nsmall=2)`%) are exclusively found in less than 1% of sampling sites; and the most common plant (*`r most_common_plant`*) and pollinator (*`r most_common_poll`*) species are only found in `r format(round(most_common_plant_percent, 2), nsmall=2)`% and `r format(round(most_common_poll_percent, 2), nsmall=2)`% of sampling sites, respectively.

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
#Taxonomic coverage outputs
#Find number of plant and pollinator species
##Pollinators
poll_spp = data %>% 
select(Pollinator_rank, Pollinator_accepted_name) %>% 
filter(Pollinator_rank == "SPECIES") %>% 
distinct(Pollinator_accepted_name) %>% 
nrow(.)
##Plants
plant_spp = data %>% 
select(Plant_rank, Plant_accepted_name) %>% 
filter(Plant_rank == "SPECIES") %>% 
distinct(Plant_accepted_name) %>% 
nrow(.)

#Overall plant coverage
plant_coverage = readRDS("../Data/Manuscript_info/plant_coverage.RData")

#Average plant family coverage
d1 = readRDS("../Data/Manuscript_info/plant_coverage_phylo_RData")
mean_plant_fam_cov = d1 %>% 
ungroup() %>% 
filter(fam_group =="B") %>% 
summarise(mean_plant_fam_cov = mean(Percent)) %>% 
pull()

@@

The database contains a total of `r prettyNum(plant_spp_number, big.mark=",")` plant and `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator species. The database coverage of flowering plants occurring in Europe is `r format(round(plant_coverage, 2), nsmall=2)`% (**Figure 4**), with an average coverage of `r format(round(mean_plant_fam_cov, 2), nsmall=2)`% at the plant family level. There are x% of families without recorded interactions and the absence of information seems to not follow strongly phylogenetic constraints (OUTPUT lambda)

The estimated sampling coverage of plant species at European level is x% (**Figure 4**). The three families with higher number of interactions within the database are xxxxx (%), xxxxxx (%) and xxxxx (%). Despite these species have a high number of interactions within the database, the number of species recorded within the database in comparison with the total number of species at European level reveals a low coverage of interactions for most of the species of these families.

The most common order of plants is Asterales with Asteraceae being the family with highest number of species within the database.

The database coverage of plants at European level is x% and the pollinator coverage when considering bees x%, syrphids x% and butterflies x%.

Most species of pollinators are Hymenoptera species (%), and most of these species are bees (%).

**Figure 3**
**Figure 4**
**Figure S1**
